---
title: "Caribou"
author: "Sean Wilson"
date: "24 June 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(gganimate)
```

```{r}
# Get the Data

individuals <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-23/individuals.csv')
locations <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-23/locations.csv')


```

```{r}
skimr::skim(individuals)
skimr::skim(locations)
```

What information was recorded within the individuals table?

```{r}
colnames(individuals)
```

So each animal had a unique ID, and had various metrics such as gender, life stage, and pregnancy. An interesting variable is the "death_cause", lets see what is listed within this category. 

```{r}
individuals$death_cause[!is.na(individuals$death_cause)]
```

There were 54 recorded deaths. These are broken up into categories, however a large number of these are unknown. We can still graph this and identify what the largest causes of deaths were within this cohort.  

```{r}
individuals %>% 
  filter(!is.na(death_cause)) %>% 
  ggplot(aes(death_cause, fill = death_cause)) +
  geom_bar()
```

Some interesting death causes here: not all natural! Poor animal that was hit by vehicles. This list can be broken down into 4 main categories: Accidental, Predation, Vehicle/Train collision and Unknown. There are also suspected predations, but the observer has still recorded as unknown.  


```{r}
individuals %>% 
  filter(!is.na(death_cause)) %>% 
  mutate(is.dead = !is.na(death_cause)) %>% 
  ggplot(aes(is.dead, death_cause), fill(death_cause)) +
  geom_bar(stat = "identity") +
  coord_polar() + 
  theme(axis.text.x = element_text())

p <- individuals %>% 
  filter(!is.na(death_cause)) %>% 
  mutate(is.dead = !is.na(death_cause)) %>% 
  ggplot(aes(x=is.dead, y=death_cause)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  
  # This add the bars with a blue color
  geom_bar(stat="identity", fill=alpha("blue", 0.3)) +
  
  # Limits of the plot = very important. The negative value controls the size of the inner circle, the positive one is useful to add size over each bar
  ylim(-100,120) +
  
  # Custom the theme: no axis title and no cartesian grid
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-2,4), "cm")     # This remove unnecessary margin around plot
  ) +
  
  # This makes the coordinate polar instead of cartesian.
  coord_polar(start = 0)
p
```








