---
title: "uncanny_xmen"
author: "Sean Wilson"
date: "30 June 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gganimate)
library(magick)
```


```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest!

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2020-06-30')

comic_bechdel <- tuesdata$comic_bechdel
characters <- tuesdata$characters

```

```{r}
skimr::skim(tuesdata$character_visualization)
map(tuesdata, function(x) colnames(x))
skimr::skim(tuesdata$character_visualization)
```

```{r}
tuesdata$covers$characters_visualized
tuesdata$covers$issue
```

Which character initiates the most physical conflict?

```{r}
as.data.frame(table(filter(tuesdata$characters, initiates_physical_conflict >= 0)$character)) %>% 
  mutate(Conflicts = gsub("\\=.*", "", Var1)) %>% 
  mutate(Conflicts = fct_reorder(Conflicts, desc(Freq))) %>%
  ggplot(aes(Conflicts, Freq, fill = Var1)) +
  geom_col() +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank()) +
  ylab(label = "Times Initated Physical Conflict") +
  ggtitle("Does Wolverine pick the most fights?", subtitle = "Yes, yes he does")

tuesdata$character_visualization %>% filter(depicted>0) %>% aggregate()

ggsave(filename = "phys_contact_per_character.png", dpi = 150, height = 10, width = 15)
```

Unsurprisingly, Wolverine initiates fights most frequently, followed by Storm and Cyclops

This can be graph A

```{r}
A <- as.data.frame(table(filter(tuesdata$characters, initiates_physical_conflict >= 0)$character)) %>% 
  mutate(Conflicts = gsub("\\=.*", "", Var1)) %>% 
  mutate(Conflicts = fct_reorder(Conflicts, desc(Freq))) %>%
  ggplot(aes(Conflicts, Freq, fill = Var1)) +
  geom_col() +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank()) +
  ylab(label = "Times Initated Physical Conflict") +
  ggtitle("Does Wolverine pick the most fights?", subtitle = "Yes, yes he does")
```



Can we make this an animation that flicks through the various attributes?

```{r}

as.data.frame(table(filter(tuesdata$characters, initiates_physical_conflict > 0)$character)) %>% 
  mutate(Conflicts = fct_reorder(Var1, desc(Freq))) %>%
  ggplot(aes(Conflicts, Freq, fill = Var1)) +
  geom_col() +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none")

as.data.frame(table(filter(tuesdata$characters, expresses_reluctance_to_fight > 0)$character)) %>% 
  mutate(Conflicts = fct_reorder(Var1, desc(Freq))) %>%
  ggplot(aes(Conflicts, Freq, fill = Var1)) +
  geom_col() +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none")
```




Heatmap of characteristics:

```{r, fig.width=10, fig.height=7}
a <- tuesdata$characters
dplyr::select_if(a, is.numeric) %>% mutate(character = characters$character) -> a
a[, -1] -> a
a[is.na(a)] <- 0 
a <- a %>%
   group_by(character) %>%
   summarise_each(funs(sum))

a <- a[, c(1, 3:18)]
a <- a %>% column_to_rownames(var = "character")
heat <- aheatmap(t(as.matrix(a)), scale = "column", treeheight = 10, distfun = "pearson", width = 8, height = 5,
                 filename = "heatmap_characteristics.png")

```

Interestingly being captured and eating food cluster together, which would indicate that these happen together quite often. Clothing being torn is also associated here, which does make sense as being caputured could easily involve torn clothes.

Lets see who has the most appearances on the cover:

```{r}
tuesdata$covers$characters_visualized %>% str_split(pattern = "\r\n")

data.frame(issue = tuesdata$covers$issue, n_characters = sapply(X = tuesdata$covers$characters_visualized %>% str_split(pattern = "\r\n"), FUN = length)) %>% ggplot(aes(issue, n_characters)) +
  geom_violin() +
  geom_jitter()
```

The cover has fewer, rather than more, characters portrayed.  

```{r}
df <- tuesdata$covers$characters_visualized %>% str_split(pattern = "\r\n")
names(df) <- tuesdata$covers$issue
df
temp <- data.frame()
for (i in 1:length(df)) {
  df1 <- data.frame(issue = names(df[i]), character = df[i])
  colnames(df1) <- c("issue", "character")
  temp <- rbind(temp, df1)
}
temp$count <- 1
table(temp$character)

temp
```


Lets look at how each character is used.

```{r depictions}

b <- tuesdata$character_visualization

b <- b %>%
   group_by(character, costume) %>%
   #summarise_each(funs(sum)) %>% 
   mutate(character = gsub("\\=.*", "", character)) %>% 
  mutate(character = gsub("\\(.*", "", character))
temp <- b

b_format <- b %>% 
  filter(character != "Omnipresent narration", character != "Editor narration") %>%
  group_by(issue, character) %>% 
  mutate(costume = NA) %>% 
  summarise_each(funs = sum) %>% 
  ungroup() %>% 
  group_by(character) %>% 
  mutate(total = cumsum(depicted)) %>% 
  group_by(issue) %>% 
  mutate(rank = rank(-total),
         #value_rel = total/total[rank==1],
         value_lbl = paste0(" ", round(total))) %>% 
  group_by(character) %>% 
  filter(rank<=10) %>% 
  ungroup() 

staticplot <- ggplot(b_format, aes(rank, group = character, 
                fill = as.factor(character), color = as.factor(character))) +
  geom_tile(aes(y = total/2,
                height = total,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(character, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y=total,label = value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=22, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=15, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"))

animation <- staticplot + transition_states(issue, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  + ease_aes('cubic-in-out') +
  labs(title = 'Most Depicted Characters',  
       subtitle  =  "Top Cumulative Depictions by Issue {closest_state}",
       caption  = "Total depictions | Data Source: @ClaremontRun") 


animate(animation, 500, fps = 30,  width = 400, height = 400, 
        renderer = gifski_renderer("depicted.gif"))

```


```{r speech}

b <- tuesdata$character_visualization

b <- b %>%
   group_by(character, costume) %>%
   #summarise_each(funs(sum)) %>% 
   mutate(character = gsub("\\=.*", "", character)) %>% 
  mutate(character = gsub("\\(.*", "", character))
temp <- b

b_format <- b %>% 
  filter(character != "Omnipresent narration", character != "Editor narration") %>%
  group_by(issue, character) %>% 
  mutate(costume = NA) %>% 
  summarise_each(funs = sum) %>% 
  ungroup() %>% 
  group_by(character) %>% 
  mutate(total = cumsum(speech)) %>% 
  group_by(issue) %>% 
  mutate(rank = rank(-total),
         #value_rel = total/total[rank==1],
         value_lbl = paste0(" ", round(total))) %>% 
  group_by(character) %>% 
  filter(rank<=10) %>% 
  ungroup() 

staticplot <- ggplot(b_format, aes(rank, group = character, 
                fill = as.factor(character), color = as.factor(character))) +
  geom_tile(aes(y = total/2,
                height = total,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(character, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y=total,label = value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=22, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=15, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"))

animation <- staticplot + transition_states(issue, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  + ease_aes('cubic-in-out') +
  labs(title = 'Most Spoken Characters',  
       subtitle  =  "Top Cumulative Speech by Issue {closest_state}",
       caption  = "Total speech | Data Source: @ClaremontRun") 


spe <- animate(animation, 500, fps = 30,  width = 400, height = 400, 
        renderer = gifski_renderer())
spe
```


```{r thoughts}

b <- tuesdata$character_visualization

b <- b %>%
   group_by(character, costume) %>%
   #summarise_each(funs(sum)) %>% 
   mutate(character = gsub("\\=.*", "", character)) %>% 
  mutate(character = gsub("\\(.*", "", character))
temp <- b

b_format <- b %>% 
  filter(character != "Omnipresent narration", character != "Editor narration") %>%
  group_by(issue, character) %>% 
  mutate(costume = NA) %>% 
  summarise_each(funs = sum) %>% 
  ungroup() %>% 
  group_by(character) %>% 
  mutate(total = cumsum(thought)) %>% 
  group_by(issue) %>% 
  mutate(rank = rank(-total),
         #value_rel = total/total[rank==1],
         value_lbl = paste0(" ", round(total))) %>% 
  group_by(character) %>% 
  filter(rank<=10) %>% 
  ungroup() 

staticplot <- ggplot(b_format, aes(rank, group = character, 
                fill = as.factor(character), color = as.factor(character))) +
  geom_tile(aes(y = total/2,
                height = total,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(character, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y=total,label = value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=22, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=15, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"))

animation <- staticplot + transition_states(issue, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  + ease_aes('cubic-in-out') +
  labs(title = 'Visually Thoughtful Characters',  
       subtitle  =  "Top Cumulative Seen Thoughts by Issue {closest_state}",
       caption  = "Total thoughts | Data Source: @ClaremontRun") 


th <- animate(animation, 500, fps = 40,  width = 400, height = 400, 
        renderer = gifski_renderer())
th
```

```{r narrative}

b <- tuesdata$character_visualization

b <- b %>%
   group_by(character, costume) %>%
   #summarise_each(funs(sum)) %>% 
   mutate(character = gsub("\\=.*", "", character)) %>% 
  mutate(character = gsub("\\(.*", "", character))
temp <- b

b_format <- b %>% 
  filter(character != "Omnipresent narration", character != "Editor narration") %>%
  group_by(issue, character) %>% 
  mutate(costume = NA) %>% 
  summarise_each(funs = sum) %>% 
  ungroup() %>% 
  group_by(character) %>% 
  mutate(total = cumsum(narrative)) %>% 
  group_by(issue) %>% 
  mutate(rank = rank(-total),
         #value_rel = total/total[rank==1],
         value_lbl = paste0(" ", round(total))) %>% 
  group_by(character) %>% 
  filter(rank<=10) %>% 
  ungroup() 

staticplot <- ggplot(b_format, aes(rank, group = character, 
                fill = as.factor(character), color = as.factor(character))) +
  geom_tile(aes(y = total/2,
                height = total,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(character, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y=total,label = value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=22, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=15, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"))

animation <- staticplot + transition_states(issue, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  + ease_aes('cubic-in-out') +
  labs(title = 'Most Narrated Characters across time',  
       subtitle  =  "Top Cumulative Narrations by Issue {closest_state}",
       caption  = "Total narrative | Data Source: @ClaremontRun") 


nar <- animate(animation, 500, fps = 30,  width = 400, height = 400, 
        renderer = gifski_renderer())

```

Use magick to pull the animations together. all have the same settings so will flow well. 

```{r magick}
a_mgif <- image_read(dep)
b_mgif <- image_read(spe)
c_mgif <- image_read(th)
d_mgfi <- image_read(nar)

new_gif <- image_append(c(a_mgif[1], b_mgif[1], c_mgif[1], d_mgif[1]))
for(i in 2:500){
  combined <- image_append(c(a_mgif[i], b_mgif[i], c_mgif[i], d_mgif[i]))
  new_gif <- c(new_gif, combined)
}

new_gif
```




Time course of depictions of speech vs thought across time

```{r}
b <- tuesdata$character_visualization

b <- b %>%
   group_by(character, costume) %>%
   #summarise_each(funs(sum)) %>% 
   mutate(character = gsub("\\=.*", "", character)) %>% 
  mutate(character = gsub("\\(.*", "", character))
temp <- b

format_sp_th <- b %>% 
  filter(character != "Omnipresent narration", character != "Editor narration") %>%
  group_by(issue, character) %>% 
  mutate(costume = NA) %>% 
  summarise_each(funs = sum) %>% 
  ungroup() %>% 
  group_by(character) %>% 
  mutate(total.speech = cumsum(speech), total.thought = cumsum(thought), total.depicted = cumsum(depicted)) %>% 
  group_by(issue) %>% 
  mutate(rank = rank(-total.depicted),
         #value_rel = total/total[rank==1],
         value_lbl = paste0(" ", character)) %>% 
  group_by(character) %>% 
  filter(rank<=10) %>% 
  ungroup() 

staticplot <- ggplot(format_sp_th, aes(total.speech, total.thought, group = character, 
                fill = as.factor(character), color = as.factor(character))) +
 
  geom_text(aes(y = 0, label = paste(character, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y=total.depicted,label = value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=22, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=15, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"))

animation <- staticplot + transition_states(issue, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  + ease_aes('cubic-in-out') +
  labs(title = 'Speech vs Thought across issues',  
       subtitle  =  "Cumulative as of Issue {closest_state}",
       caption  = "Speech vs Thought | Data Source: @ClaremontRun") 


spvsth <- animate(animation, 500, fps = 30,  width = 400, height = 400, 
        renderer = gifski_renderer())
```




```{r}
b <- tuesdata$character_visualization

b <- b %>%
   group_by(character, costume) %>%
   summarise_each(funs(sum)) %>% 
   mutate(character = gsub("\\=.*", "", character)) %>% 
  mutate(character = gsub("\\(.*", "", character))
  

b
colnames(b)
b <- b %>% pivot_longer(cols = c("speech", "thought", "narrative", "depicted"))


b %>% filter(character != "Omnipresent narration", character != "Editor narration") %>% 
  ggplot(aes(character, value, fill = character)) +
  geom_bar(stat="identity") +
  facet_wrap(~name, scales = "free_x") +
  coord_flip() +
  theme(legend.position = "none") 
  
n <- b %>% filter(character != "Omnipresent narration", character != "Editor narration") %>% 
  ggplot(aes(character, value, fill = name)) +
  geom_bar(stat="identity", position = "stack") +
  coord_flip()

c <- b %>% filter(character != "Omnipresent narration", character != "Editor narration") %>% 
  ggplot(aes(character, value, fill = name)) +
  geom_bar(stat="identity", position = "fill") +
  coord_flip() + 
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())

d <- b %>% filter(character != "Omnipresent narration", character != "Editor narration") %>% 
  ggplot(aes(character, value, fill = costume)) +
  geom_bar(stat="identity", position = "fill") +
  coord_flip() + 
  theme(axis.text.y = element_blank(),
        aaxis.title.y = element_blank())

n + c + patchwork::plot_layout(guides = "collect")
```








